\documentclass[12pt,letterpaper]{ryerson}

\input{variables}
\interdisplaylinepenalty = 2500


\usepackage[inline]{enumitem}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref} 
\usepackage{graphicx}
\usepackage{array, makecell}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage[title]{appendix}
\usepackage{blindtext}
\usepackage[font=small,labelfont=bf,skip=5pt]{caption}
\usepackage{charter}
\usepackage{float}
\input{insbox.tex}
\usepackage{titlesec}
\usepackage{apptools}
\usepackage{tabularx}

\titleformat{\chapter}[display]{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}   
\titlespacing*{\chapter}{0pt}{-10pt}{25pt}

\renewcommand{\ttdefault}{Computer Modern}
\newcommand\Tstrut{\rule{0pt}{2.6ex}}         % = `top' strut
\newcommand\Bstrut{\rule[-0.9ex]{0pt}{0pt}}   % = `bottom' strut

\AtAppendix{\titleformat{\chapter}[block]{\LARGE\bfseries}{\appendixname~\thechapter:}{0.333em}{}%
\titlespacing*{\chapter}{0pt}{-20pt}{40pt}}

\setAuthor{Moeen Bagheri}
\setTitle{\textbf{Multi-Step Sales Forecasting of Walmart Products}}
\setThesisDegree{Master of Science (MSc)}
\setUniversity{Ryerson University}
\setDepartment{Data Science and Analytics}
\setLocation{Toronto, Ontario, Canada}
\setThesisYear{2020}

\setAuthorsDeclaration{
I hereby declare that I am the sole author of this MRP. This is a true copy of the MRP, including any required final revisions. \newline

\noindent I authorize Ryerson University to lend this MRP to other institutions or individuals for the purpose of scholarly research. \newline

\noindent I further authorize Ryerson University to reproduce this MRP by photocopying or by other means, in total or in part, at the request of other institutions or individuals for the purpose of scholarly research. \newline

\noindent I understand that my MRP may be made electronically available to the public. \newline

\noindent Moeen Bagheri
}

\setAbstract{
\input{chapters/0_abstract}
}
\setAcknowledgements{I am very thankful of \textbf{Dr. Konstantinos Georgiou} for his continuous support and assistance during the semester. Dr. Georgiou provided me with valuable feedback and helped me with thinking critically about the problem. He also provided valuable comments regarding the structure and contents of the paper. I am grateful to Dr. Georgiou for making this project a reality.
}


\begin{document}

\begin{ryerson}
\chapter{Introduction}
\input{chapters/1_Introduction}

\chapter{Literature Review}
\input{chapters/2_literature_review}


\chapter{Exploratory Data Analysis}
\input{chapters/3_exploratory_data_analysis}


\chapter{Methodology}
\input{chapters/4_methodology}


\chapter{Results}
\input{chapters/5_results}


\chapter{Discussion}
\input{chapters/6_discussion}


\chapter{Conclusions and Future Work}
\input{chapters/7_conclusions}


\end{ryerson}

\begin{appendices}
\end{appendices}
\appendix
\input{appendix/tables}
\input{appendix/figures}

\bibliographystyle{ieeetr}
\bibliography{references}

\end{document}
